SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-15 docs/questioning.tex
tiny fix
some changes / fixes in the intro

\begin{IEEEkeywords}
Security and Protection, Web Application Security, Code injection Attacks,
Testing, Cross-Site Scripting.
\end{IEEEkeywords}

@@

There is already a survey on mitigating software vulnerabilities in
general~\cite{SZ12}. The scope of that research is much broader that
ours and leaves out the majority of the approaches and mechanisms that
we consider in this work. This is mainly because that work includes
countermeasures that identify vulnerabilities using program analysis
(which takes place during the development or testing phases), while we
consider protection mechanisms that counter web attacks when they take
place. Similarly, static or dynamic analysis techniques that examine
applications to identify vulnerabilities that may lead to the attacks
that we described earlier are out of scope as well. While
countermeasures against {\sc sql} injection attacks have been
previously surveyed in a 2006 paper~\cite{HVO06}, a significant number
of new {\sc sql} injection defenses has been proposed since then, as
we mentioned earlier.

@@

Injection attacks that involve {\sc dsl}s constitute an important
subset of the code injection problem, as {\sc dsl}s such as
{\sc sql} and {\sc xml} play a significant role in the development of
both web and mobile applications. For example, many applications have
interfaces through which a user enters input to interact with the
application, thereby interacting with the underlying database. This
input can become part of an {\sc sql} query and get executed on the
target database. Code injection attacks that exploit vulnerabilities
in database interfaces by taking advantage of input validation issues,
such as incorrectly passed parameters or incorrect type handling, are
called {\sc sql} injection attacks~\cite{CERT02,MS09,HVO06,SW06}.
Consider a trivial exploit that takes advantage of incorrectly
filtered quotation characters in an application that sends a temporary
password for a forgetful user via email by executing the following
query:

@@

\noindent
Attackers that would input the string {\tt anything' OR 'x'='x}
thereby obtaining the administrator's password by email. Savvy
programmers can use certain {\sc api} functions, such as {\sc php}'s
{\tt mysql\_real\_escape\_string()}, to detect malformed input, or,
better, use prepared {\sc sql} statements instead of statement
templates. Unfortunately, the increasing number of {\sc sql} injection
attacks suggests that programmers are not always that careful. Using
similar techniques, malicious users can mount other exploits based on
{\sc dsl}s such as {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc
  xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. The effects can be
wide-ranging. A malicious user can view sensitive information, destroy
or modify protected data, or even crash the entire application.

{\sc html} is another {\sc dsl} that can be used for malicious
purposes when an application does not properly handle user-supplied
data. Based on this vulnerability attackers can supply valid {\sc
  html}, typically via a parameter value, and inject their own content
into the page. {\sc html} injection is mainly associated with {\sc
  xss} attacks~\cite{BJM08,LZRL09}. An {\sc xss} attack based on
{\sc html} injection though, can also be used as a
vehicle for a {\sc csrf} attack. Consider a bulletin board system where
{\tt img} tags are not checked. A malicious user could embed a {\sc
  csrf} request within an {\tt img} tag in the following manner:

@@

There are three main categories of etiological approaches used to protect web
applications against injection attacks:
\emph{Parse-Tree Validation},
\emph{Policy Enforcement}, and
\emph{Instruction Set Randomization} ({\sc isr})}.

>>>>

\begin{IEEEkeywords}
Protection Mechanisms, Web Application Security, Code injection Attacks,
Testing, Cross-Site Scripting.
\end{IEEEkeywords}

@@

There is already a survey on mitigating software vulnerabilities in
general~\cite{SZ12}. The scope of that research is much broader than
ours and leaves out the majority of the approaches and mechanisms that
we consider in this work. This is mainly because that work includes
countermeasures that identify vulnerabilities using program analysis
(which takes place during the development or testing phases), while we
consider protection mechanisms that counter web attacks when they take
place. Similarly, static or dynamic analysis techniques that examine
applications to identify vulnerabilities that may lead to the attacks
that we described earlier are out of scope as well. While
countermeasures against {\sc sql} injection attacks have been
previously surveyed in a 2006 paper~\cite{HVO06}, a significant number
of new {\sc sql} injection defenses has been proposed since then, as
we mentioned earlier.

@@

Injection attacks that involve {\sc dsl}s constitute an important
subset of the code injection problem, as {\sc dsl}s such as
{\sc sql} and {\sc xml} play a significant role in the development of
both web and mobile applications. For example, many applications have
interfaces through which a user enters input to interact with the
application, thereby interacting with the underlying database. This
input can become part of an {\sc sql} query and gets executed on the
target database. Code injection attacks that exploit vulnerabilities
in database interfaces by taking advantage of input validation issues,
such as incorrectly passed parameters or incorrect type handling, are
called {\sc sql} injection attacks~\cite{CERT02,MS09,HVO06,SW06}.
Consider a trivial exploit that takes advantage of incorrectly
filtered quotation characters in an application that sends a temporary
password for a forgetful user via email by executing the following
query:

@@

\noindent
Attackers that would input the string {\tt anything' OR 'x'='x}
would obtain the administrator's password by email. Savvy
programmers can use certain {\sc api} functions, such as {\sc php}'s
{\tt mysql\_real\_escape\_string()}, to detect malformed input, or,
better, use prepared {\sc sql} statements instead of statement
templates. Unfortunately, the increasing number of {\sc sql} injection
attacks suggests that programmers are not always that careful. Using
similar techniques, malicious users can mount other exploits based on
{\sc dsl}s such as {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc
  xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. The effects can be
wide-ranging. A malicious user can view sensitive information, destroy
or modify protected data, or even crash the entire application.

{\sc html} is another {\sc dsl} that can be used for malicious
purposes when an application does not properly handle user-supplied
data. Based on this vulnerability attackers can supply valid {\sc
  html}, typically via a parameter value, and inject their own content
into the application's page. {\sc html} injection is mainly associated with {\sc
  xss} attacks~\cite{BJM08,LZRL09}. An {\sc xss} attack based on
{\sc html} injection though, can also be used as a
vehicle for a {\sc csrf} attack. Consider a bulletin board system where
{\tt img} tags are not checked. A malicious user could embed a {\sc
  csrf} request within an {\tt img} tag in the following manner:

@@

There are three main categories of etiological approaches used to protect web
applications against injection attacks:
\emph{Parse-Tree Validation},
\emph{Policy Enforcement}, and
\emph{Instruction Set Randomization} ({\sc isr}).
